### 2016-08-29 ms/ms.tex
added conceptual figure to supplement

%% Lauren I like this paragraph, but I think we could use a figure in
%% the supplementary to help the reader understand... maybe a
%% schematic representation? I'll try and think of something
Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species. We
develop a method examine the temporal turnover of interactions
weighted based on their similarity. We followed \cite{ahn2010link}
algorithm to hierarchically cluster all the interactions (edges)
across sites and years based on their similarity, and build a
dendrogram. The interaction similarity is based how may plants and
pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

We would like to thank Paulo Guimar{\~a}es and Aaron Clauset for their
invaluable discussions, and Leto Peel for help with the change point
analysis.  We thank the growers and land owners that allowed us to
work on their property. We also greatly appreciate the identification
assistance of expert taxonomists Martin Hauser, Robbin Thorp and Jason
Gibbs.  This work was supported by funding from the Army Research
Office (W911NF-11-1-0361 to CK), the Natural Resources Conservation
Service (CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship, the USDA
NIFA Graduate Fellowship, and the Berkeley Institute for Data
Science. Funding for MPG was provided by S{\~a}o Paulo Research
Foundation (FAPESP, grant 2013/13319-5). We also appreciate the Santa
Fe Institute for faciliting this international collaboration.

>>>>

Though species may turnover across years, some groups of species may
essentially replace each other if they fill similar roles in the
network, ocupying the same network position and interacting with
similar species. At non-assembling communities, species turnover may
overestimate the temporal changes in the networks if the interactions
occurring in one year are similar to those in the next year when they
are weighted by the similarity of their constituent species
(Fig.~S1). We develop a method examine the temporal turnover of
interactions weighted based on their similarity. We followed
\cite{ahn2010link} algorithm to hierarchically cluster all the
interactions (edges) across sites and years based on their similarity,
and build a dendrogram. The interaction similarity is based how may
plants and pollinators (vertices) two edges share \citep{ahn2010link,
  kalinka2011linkcomm}. The more species edges shared in common, the
shorter the branch length between them on the dendrogram.  We next
calculated the temporal turnover of interactions weighted by their
similarity, as approximated by ``phylogenetic'' distance
\citep{graham2008phylogenetic, picante-2010-1463}. When then use
linear models to test whether the weighted turnover of interactions
varied between assembling and non-assembling networks \citep{lme4,
  lmetest}.

@@

We would like to thank Paulo Guimar{\~a}es, Aaron Clauset and Matthew
Hutchinson for their invaluable discussions and comments, and Leto
Peel for help with the change point analysis.  We thank the growers
and land owners that allowed us to work on their property. We also
greatly appreciate the identification assistance of expert taxonomists
Martin Hauser, Robbin Thorp and Jason Gibbs.  This work was supported
by funding from the Army Research Office (W911NF-11-1-0361 to CK), the
Natural Resources Conservation Service (CIG-69-3A75-12-253,
CIG-69-3A75-9-142, CIG-68-9104-6-101 and WLF-69-7482-6-277 to The
Xerces Society), the National Science Foundation (DEB-0919128 to CK),
The U.S.  Department of Agriculture (USDA-NIFA 2012-51181-20105 to
Michigan State University).  Funding for LCP was provided by an NSF
Graduate Research Fellowship, the USDA NIFA Graduate Fellowship, and
the Berkeley Institute for Data Science. Funding for MPG was provided
by S{\~a}o Paulo Research Foundation (FAPESP, grant 2013/13319-5). We
also appreciate the Santa Fe Institute for faciliting this
international collaboration.
